% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Career}{\faSuitcase}

%\renewcommand{\labelitemi}{$\bullet$}


\begin{experiences}

\consultantexperience
  {Present} {Principal Engineer (Investment Planning)}{\weblink{https://www.tmr.qld.gov.au}{Transport and Main Roads}}{North Coast Region}
  {May 2025} {State Roads Authority}{Investment Planning}
  {
    \begin{itemize}
\item Lead early-stage development of major transport infrastructure and government election commitments, aligning with ATAP, OnQ and PAF frameworks to progress projects through structured stage-gates.
\item Coordinate cross-functional subject matter experts (engineering, environmental, cultural heritage, geotechnical, finance) to define problem statements, assess options and prepare investment documentation that informs executive decision-making.
\item Facilitate risk and scope definition workshops, validating cost, schedule and delivery assumptions to ensure robust feasibility assessments.
\item Manage multidisciplinary consultants and internal teams through the development phase, integrating technical, operational and commercial inputs into coherent investment cases.
\item Direct procurement and contract management of technical services in line with governance and probity requirements, achieving value-for-money outcomes.
\item Provide strategic reporting to senior executives on development progress, approvals and risks to support transparent, evidence-based investment decisions.
    \end{itemize}
  }
  {Investment Planning, Project Development, Project Management, Business Case Preparation, Risk Management, Governance, Stakeholder Engagement}
\emptySeparator

\consultantexperience
  {May 2025}    {Senior Engineerr (Civil)}{\weblink{https://www.tmr.qld.gov.au/}{Transport and Main Roads}}{North Coast Region}
  {December 2023}   {State Roads Authority}{Maintenance, Assets \& Traffic Engineering team}
  {                 
  
    \begin{itemize}
    \item Led strategic asset management and capital planning for regional bridge and culvert networks valued at \$2.5B, integrating risk, cost and performance considerations.
    \item Directed procurement, contract administration and delivery of structural renewal projects, ensuring compliance with technical standards and governance requirements.
    \item Coordinated multidisciplinary specialists (structural, environmental, geotechnical) to assess risks, plan interventions and maintain network reliability.
    \item Managed stakeholder engagement with local government, contractors and Indigenous partners to align project outcomes and address cultural heritage and native title considerations.
    \item Contributed to statewide structures management governance frameworks, supporting prioritisation and lifecycle optimisation across asset portfolios.
     
    \end{itemize}
        \vspace{0.5em}
     \textbf{Higher duty roles (2024-2025):}
    \begin{itemize}
     \item \textbf{Strategic Planning (Dec 2024):} Provided specialist input on infrastructure constraints and planning considerations for SEQ2023 and Major Enterprise and Industry Area designations.
    \item \textbf{Project Planning (Jan 2024):} Directed preparation of short-form link plan documentation and contributed to tender evaluation for an Options Analysis stage of a bypass project.
    \item \textbf{Design - Technical Services (May 2024):} Reviewed and approved technical designs for compliance with TMR standards, assessing safety, operational and regulatory requirements.
    \item \textbf{Assets (Apr 2025):} Led civil structures asset team, overseeing staff performance, stakeholder messaging, and cross-business coordination of asset planning activities.
   
    \end{itemize}
    \vspace{0.5em}
    \
  }
  {Asset Management, Lifecycle Planning, Risk Assessment, Program Management, Governance, Stakeholder Engagement}

\emptySeparator

  \consultantexperience
	{November 2023}    {Senior Engineer (Civil)}{\weblink{https://recor.au}{RECOR}}{Noosa}
	{June 2021}   {Civil/Structural Engineers \& Project Managers.}{Civil Engineering team}
	{                  
		\begin{itemize}
			\item Directed multidisciplinary project development from concept through to regulatory approval and delivery, integrating engineering, commercial, and stakeholder inputs.
			\item Managed sub-consultants and internal teams across planning, design and approvals, balancing scope, cost, risk and stakeholder expectations.
			\item Established and led the civil engineering discipline, providing RPEQ supervision and embedding ISO-certified governance systems (Quality, Safety, Environment).
			\item Prepared technical documentation, feasibility assessments and submissions to support client and regulator decision-making.
			\item Engaged with local councils, government agencies and contractors to secure approvals, manage community expectations, and ensure projects met environmental and network requirements.
			\item Prepared clear technical reports, documentation and submissions to support approvals and stakeholder decision-making.
\end{itemize}
}
{Project Management, Project Governance, Concept Development, Multidisciplinary Coordination, Regulatory Approvals, Leadership, Commercial}
	\emptySeparator   

  \consultantexperience
  {June 2021}    {Project Management Engineer}{\weblink{https://www.pavement.com.au}{Pavement Management Services}}{Sunshine Coast}
  {October 2020}   {Specialist engineers in pavement solutions.}{Network Projects team}
  		{                 
                      \begin{itemize}
	\item Managed network-level pavement asset projects for local and state government, integrating condition data, deterioration modelling and lifecycle analysis to optimise investment programs.
	\item Led stakeholder engagement to align project scope, expectations and deliverables across technical and management teams.
	\item Developed research into emerging technologies and prepared technical papers for industry publication (IPWEA).

                      \end{itemize}
                    }
                    {Project Management, Asset Analytics, Project Management, Deterioration Modelling, Stakeholder Engagement}
  \emptySeparator     

  \consultantexperience
    {October 2020}   {Information Analyst}{\weblink{https://www.usc.edu.au}{University of the Sunshine Coast}}{Sunshine Coast}
    {July 2018}  {Australian University}{Strategic Information and Analysis team}
    {
                      \begin{itemize}
		\item Led requirements analysis and development of strategic financial forecasts and predictive models to support executive decision-making, resource allocation, and Commonwealth funding submissions.
		\item Provided commercial and analytical advice to executives and department heads, translating complex data into clear financial and operational insights that informed strategic planning.
		\item Collaborated with senior stakeholders across Finance, Marketing, and Academic divisions to assess market trends, enrolment drivers, and investment risks.
		\item Developed and automated performance dashboards and data pipelines using R and Python, improving data quality, reducing manual processing, and enhancing real-time reporting capability.
		\item Delivered actionable insights that guided university-wide strategic initiatives, aligning financial performance with institutional objectives and government policy frameworks.
		                                                           
                      \end{itemize}
                    }
                    {Financial Forecasting, Predictive Analytics, Commercial Advisory, Strategic Planning, Executive Reporting, R, Python, Data Visualisation}
  \emptySeparator
  \consultantexperience
    {July 2018} {Technical Officer}{\weblink{https://www.noosa.qld.gov.au}{Noosa Council}}{Noosa}
    {July 2016}   {Local Council for the Noosa Shire}{Asset Management team}
      {
                      \begin{itemize}
		\item Engagement with operational and capital works departments to compile 5 year pavement reseal program and find efficiencies with major projects team.
		\item Managed procurement processes including tender preparation, evaluation, and contractor selection, overseeing contract administration and performance management to deliver value for money outcomes.
		\item Led development of a risk-based model in R to optimise network inspection campaigns and inform decision makers and funding decisions.
		\item Led cross-departmental stakeholder engagement to implement new asset management processes, coordinating with operational teams and senior management to drive organizational change and secure buy-in across competing priorities
%		\item Developed organisation wide data collection standards and supported NDRRA funding submissions.         
		
		                                                      
                      \end{itemize}
                    }
                    {Asset Management, Risk management, Deterioration Modelling, Program Management, Disaster Recovery, Procurement}
  \emptySeparator
  \consultantexperience
    {March 2016}     {Project Manager (Asset Management)}{\weblink{https://www.vinci.com/vinci.nsf/en/index.htm}{VINCI SA} \ - \weblink{http://www.soletanchefreyssinet.com}{Soletanche-Freyssinet}}{Paris, France}
    {October 2012}   {Global construction company with expertise in specialised building, civil, hydraulic, and electrical engineering}{Asset Solutions team}
      {
                      \begin{itemize}
\item Led international asset management and infrastructure development projects across Europe, the Middle East, and North America, coordinating planning, resourcing, subcontractor management, financial reporting, and technical delivery.
\item Directed early-phase project definition and concept development for government and concession clients, aligning technical feasibility, operational risk, and commercial outcomes.
\item Developed and implemented inspection, maintenance,  monitoring and lifecycle planning frameworks for major bridges, tunnels, highways, and water infrastructure, integrating condition assessment and risk analysis to optimise reinvestment decisions.
\item Coordinated design and deployment of asset management and monitoring systems that improved data-driven decision-making and long-term asset performance.
\item Delivered technical workshops, training, and presentations to client engineering and management teams, facilitating change management in organisations to embed new practices and governance processes.
\item Led preparation of technical and commercial proposals, bid submissions, and investment documentation for infrastructure projects, supporting client capital approval processes.
\item Applied structured project management methodologies (Agile, PMBOK, PRINCE2) to manage scope, cost, schedule, risk, and quality across complex, multidisciplinary projects.

                     \end{itemize}
                    }
                    {Project Management, Leadership, Stakeholder engagement, Contract management, Civil Engineering, Asset Management, Structural Inspections, Technical Reporting}
  \emptySeparator
  \consultantexperience
  {October 2012}       {Civil Engineer}{\weblink{https://ndc.com.au}{Newton Denny Chapelle}}{Lismore}
  {March 2010}      {Town Planning/Civil Engineering/Surveying consultancy for industrial, residential and commercial developments.}{Civil Engineering team}
                    {Concept and detailed engineering for development and planning projects.
           \begin{itemize}
           \item Preparation of detailed technical reports to support development applications and planning requirements
	%	\item Engineering modelling for hydrologic and hydraulic systems, and network traffic models
		\item Leading design of subdivisions earthworks, roads, and stormwater networks for urban and rural commercial, industrial and residential developments.
		\item Undertaking design in  compliance with all relevant standards and regulations, and supervision of construction to ensure comformity with approvals
		\item Collaborating and liaising with town planners, surveyors, environmental consultants, contractors and local councils to achieve regulatory approvals
	%	\item Coordination of sub-consultants and contractors to ensure delivery of development projects

               \end{itemize}
                    }
                    {Civil Design, Urban Development, Stormwater Modelling, Road \& Pavement Design, Earthworks, Traffic Studies, CivilCAD, MUSIC, XP-Rafts, SIDRA, Site Supervision, Technical Reporting}
  \emptySeparator
  

       
\end{experiences}
