% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Ben Parry
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section compétences
\sectionTitle{Skills}{\faTasks}

\begin{keywords}

\keywordsentry{Asset Management \& Lifecycle Planning}{Strategic asset management of major infrastructure portfolios including bridges, culverts, pavements and linear networks valued at \$2.5B+. Expertise in condition assessment methodologies, deterioration modeling, risk-based prioritization and lifecycle optimization. Experience developing asset performance frameworks, reinvestment strategies and capital works programs that balance reliability, cost and network resilience. Applied knowledge of asset management standards (AS5130, ISO55000 framework).\\}

\keywordsentry{Data Analytics \& Performance Optimization}{Strong analytical capability combining engineering expertise with advanced data science skills (Graduate Diploma, Data Science). Proficient in statistical analysis, predictive modeling and data visualization using R, Python and SQL. Experienced in transforming complex asset condition data into actionable insights, optimizing intervention timing and supporting evidence-based investment decisions. Skilled in developing performance dashboards and business intelligence tools.\\}

\keywordsentry{Project \& Program Management}{Proven track record delivering complex infrastructure projects using PMBOK, PRINCE2 and Agile frameworks. Expertise in procurement, contract administration, financial oversight, risk management and program delivery across transport, civil structures and asset portfolios. Experience managing multidisciplinary teams, consultants and contractors to achieve scope, cost, schedule and quality objectives.\\}

\keywordsentry{Leadership \& Governance}{Experienced leader of engineering teams and multidisciplinary specialists, with proven capability in governance, probity and risk management. Implemented organisation-wide ISO 9001, 45001 and 14001 management systems. Active member of TMR's statewide Structures Maintenance Program Leadership Team, contributing to asset management strategy and portfolio governance.\\}

\keywordsentry{Stakeholder Engagement}{Skilled in engaging with diverse stakeholders including government agencies, Indigenous partners, contractors and community groups. Experienced in building trust, managing competing priorities and navigating sensitive issues with professionalism. Proven ability to coordinate across organizational boundaries to align asset management practices and secure stakeholder buy-in.\\}

\keywordsentry{Technical Engineering Capability}{Chartered Civil Engineer (RPEQ, CPEng, NER) with expertise in structural analysis, condition assessment and infrastructure design. Level 1 \& 2 Bridge Inspection certified. Strong understanding of structural health monitoring, non-destructive testing, failure modes analysis and engineering standards (AS5100, AS5130, TMR Technical Standards). Experience applying whole-of-life cost assessments and value-for-money analysis to asset investment decisions.\\}

\keywordsentry{Reporting \& Communication}{Experienced in preparing clear technical reports, asset management plans, business cases and executive briefings. Skilled in translating complex engineering and analytical findings into accessible recommendations for decision-makers. Proven ability to present at technical forums, chair stakeholder meetings and prepare submissions for regulators and funding bodies.\\}

\keywordsentry{Software \& Systems}{
    \begin{itemize}
        \item \textbf{Asset Management \& Enterprise Systems:} SAP ERP, Technology One, Oracle, AgileAssets, AssetWise
        \item \textbf{Data Analytics:} R, Python, SQL, Excel (advanced), Power BI, Tableau
        \item \textbf{Engineering \& CAD:} 12D, AutoCAD, TUFLOW, MUSIC, SpaceGASS, STRAND7
        \item \textbf{GIS:} QGIS, ArcGIS, MapInfo
        \item \textbf{Project Management:} MS Project, Primavera, 3PCM
\end{itemize}}

\end{keywords}



%\textbf{Java} (\textbf{JEE}, \textbf{JSE}, JME, Java Card Platform), Microsoft .Net (\textbf{C\#}), \textbf{Typescript}, Javascript, CSS}