% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

\textbf{Demonstrated knowledge and experience in providing technical advice and guidance on design and construction of road infrastructure projects.}

\par{
	In my current role as senior civil engineer with RECOR, I am responsible for overseeing the design team on all civil projects including commercial and industrial developments, residential subdivisions and urban development typically involving road and pavement design. I coordinate and provide advice and guidance to the client before and during the project, as well as to the civil team of other engineers and designers to deliver projects successfully. I have experience working in 12D to design internal roads, as well as developing pavement profiles based on local geotechnical conditions and expected traffic demands using CBR methods and familiarity with CIRCLY. I have a developed knowledge of pavements through my previous roles in asset management with understanding of pavement construction, pathologies and maintenance considerations related to the operational and strategic planning to extend the life cycle of roads while reducing the overall maintenance costs. \\
	
	As a specific example, I have recently provided design advice to a team within the Downer Group for flexible pavement of a haul road where geotechnical investigations found unsuitable wet subgrades, and it was necessary provide design details around the excavation and replacement of the unsuitable material and provision of geogrid to provide additional reinforcement.  \\}

\textbf{Demonstrated knowledge and experience in ensuring civil designs are suitable, appropriate and adequate for the purpose and are in accordance with relevant design standards.}

\par{
	As senior civil engineer I work closely with both internal and external stakeholders, including the client, architects, other consultants, and local authorities to ensure the designs are suitable for their purpose and in accordance with all relevant design standards. Delivering these projects involves finding a design that balances achieving the relevant local and national design standards to obtain development approval, ensuring a functional design that will meet the required level of service while also managing the anticipated costs in line with \client expectations around the design. I have experience in interpreting and applying the various applicable standards.\\
	
	Recent examples include coordinating the design of subdivisions within the Gympie Regional Council area where new roads were designed within the subdivisions servicing a total of 53 lots across 2 separate subdivisions. The design required ensuring conformance with the Gympie Regional Council planning scheme and development standards, while designing the internal roads in accordance with Austroads Guide to Road Design. 	\\}


\textbf{Demonstrated ability to maintain and apply all relevant standards, policies, guidelines and legislative requirements necessary for the design and construction of road infrastructure projects.}

\par{
	Throughout my career, I have worked on numerous road infrastructure projects both domestically and internationally including concession highways, council road networks and urban local streets. Defining and understanding the relevant standards, policies, guidelines, and legislative requirements is the first stage of any project within a new jurisdiction. To successfully operate in these diverse areas, I’ve become adept at interpreting, documenting, and applying the regulatory framework that applies within the context of the development and have wide ranging experience applying local infrastructure design standards, Austroads guidelines and best practice standards to design projects involving roads and pavements.\\
	
	As an example of my ability to maintain and apply relevant standards, policies, guidelines, and requirements I was responsible for the development and implementation of RECOR’s quality, environment and health and safety management systems. This required understanding of the ISO standards, national, state, and local legislation and internal business requirements that I incorporated to achieve certification for the organisation.	\\}


\emptySeparator 
\emptySeparator 
\emptySeparator 

\textbf{Demonstrated well developed interpersonal skills, including the ability to manage and maintain effective liaison and communication with all levels of internal and external stakeholders on all matters relating to transport infrastructure delivers activities.\\}

\par{
	In my past roles as project manager and project engineer, I have worked with diverse personnel, including project teams, suppliers, contractors, and local authorities to ensure all stakeholders are aligned and informed throughout the project cycle. For example, to keep stakeholders informed and aligned, I would coordinate project initiation meetings to define scope and specific requirements, and during the project would establish lines of communication through regular weekly progress meetings to provide updates and ensure expectations remained aligned with deliverables. I also involve stakeholders in the decision-making process wherever possible, seeking their input and feedback and incorporating it into project plans. Through the various roles I’ve operated within, I have developed excellent communication skills that allow me to convey technical information to both technical and non-technical stakeholders in an intuitive and understandable way, helping to build consensus and agreement throughout the project cycle.	\\}

\textbf{Experience in ability to perform and review pavement designs.}

\par{
	I have been involved in various projects that required me to design and review pavement designs for both new constructions and rehabilitation projects during my career. In my previous role as a Pavement Engineer, I was responsible reviewing road condition data to provide maintenance and rehabilitation strategies for capital planning and development of road reseal programs for various councils around Australia including specification of the required pavement remediations to be applied. I possess knowledge of the Australian Standards, Austroads, TMR standards and relevant guidelines around pavement design. Using this knowledge I have carried out pavement designs based on local CBR tests and expected traffic demands, and reviewed designs from CIRCLY to advise on flexible pavement specification. 	\\}

