% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)








\par{Dear Mr Zeller,\\
	\\
    I am writing to express my strong interest in the Principal Engineer (Civil) position with Transport and Main Roads (TMR). As a current TMR employee with RPEQ registration and experience in an acting Principal Engineer role, I am confident in my ability to contribute significantly to the Project Planning team's objectives. \\

	Throughout my career, I have developed a comprehensive skill set that aligns closely with the key responsibilities and requirements of this role: \\

	\begin{itemize}
		\item Makes Insightful Decisions: As project manager while working with Vinci, I was able to consistently demonstrate the ability to make informed decisions based on thorough analysis in particularly complex and challenging situations, often with conflicting or incomplete information, in order to provide clear decisions and direction to my team and project stakeholders. During my time in the role, I was responsible for establishing the overall program delivery framework for a state wide emergency repair and rebuild project in Mexico covering an area of 60,000kms and involving over 130 bridges and over 1000 sections of road, defining roles and reporting requirements at all levels from the individual sites and regions, through to the high level supervision and governance at the office of the Secretary of Transport. I undertook extensive engagement to ensure I had a clear understanding of the expectations and needs of the various parties, and delivered workshops and training to ensure that all stakeholders had clear understanding of the impacts and reasoning leading to the framework. I was effectively able to delegate and empower my team across international time zones to ensure the successful delivery within the tight time frames established under the contract.  My background will successfully allow me to contribute to the development of QTRIP, acting as principal representative for contract delivery and managing all aspects of the local road corridor and statewide network operations. \\
		\item Leads Change in Complex Environments: My experience in implementing organization-wide asset management practices at Noosa Council and ISO management systems at RECOR showcase my ability to lead change in a range of environments. Early and continuous engagement throughout these organisational changes was key to overcoming resistance and ensuring buy in and support from the team during the process. One of my first responsibilities after joining RECOR was to prepare and deliver the companies quality, health and environmental systems to achieve ISO certification. As work was being carried out in an adhoc and unstructured manner, I worked with the directors of the structural and project management arms of the company, as well as incorporating my own experience in Civil engineering to develop a system that was flexible enough to support the staff from each area through the transition to a company system that would achieve the ISO requirements and support the organisation in achieving the desired outcome as they grew. This experience will be invaluable during community and stakeholder engagement around the construction and maintenance, corridor management and support of SNO in delivering traffic operations to the district.  \\
		\item Builds Enduring Relationships: Throughout my career, particularly during my time at Vinci SA and RECOR, I have prioritized building strong relationships with diverse stakeholders. I've developed the ability to read situations, anticipate needs, and tailor messages accordingly to peoples backgrounds and subject matter exposure. My experience in negotiating and delivering projects in an international environment, as well as working with clients and various consultants to obtain and construct development approvals has honed my skills in articulating complex concepts and working towards win-win outcomes. Using these skills, I will be ideally equipped to participate and contribute to the Regional Planning Coordination Group, and build strong relationships with the wide range of stakeholders the role will demand. \\
		\item Drives Accountability and Outcomes: At RECOR and TMR, I have consistently worked collaboratively to develop clear and shared objectives that inspire collective ownership. I've demonstrated persistence through project setbacks such as development application refusals or resistance to change within organisations, working with and empowering people to step back, revise and use alternate strategies to overcome issues. My experience in managing teams and delivering projects on time and to specifications in complex environments is largely due to my ability to drive ownership and empower others to manage their responsibilities independently. This will enable me to provide leadership, guidance and management of district staff and resources to develop a highly motivated and skilled workforce all working together to achieve the districts target outcomes. \\
		\item Demonstrates Sound Governance: My roles at TMR and Noosa Council have given me a strong understanding of legislative and regulatory frameworks from the perspective of a public service organisation. As Senior Engineer for stewardship of Bridges in the North Coast District, as well as my time as an Asset management officer with Noosa Council, I've consistently acted in the interests of the community and organization, particularly when procuring goods and services and implementing rehabilitation programs to ensure that the public funding is utilised in a way that will deliver most benefit to the community. My experience in asset management, income forecasting and risk analysis has equipped me to work closely with partners to analyse trends and forecast long-term risks, develop contingencies and ensure program outcomes are achieved. With this experience, I will be confident in ensuring efficient use of business service resources to deliver the districts operational functions and delivering value for money results across the portfolio. \\
		\item Program and Project Management: My diverse experience spans the entire project lifecycle, from planning and design to construction and asset management. At Vinci SA, I managed international projects delivering asset management solutions for major infrastructure, including bridges, tunnels, and highways across the world. This background, combined with my current role at TMR, has given me a comprehensive understanding of program management principles as applied to a state roads infrastructure organization. As an experienced project manager with program management experience through my roles, I'm fully prepared to ensure all program and project commitments are delivered locally to achieve state wide performance targets. \\

	I am particularly drawn to this opportunity because it allows me to combine my passion for infrastructure development and asset management with my commitment to serving the community. The role's emphasis on delivering high-quality outcomes for the people of Queensland resonates strongly with my professional values and aspirations. I am excited about the possibility of contributing to TMR's mission and would welcome the opportunity to discuss how my skills and experience can benefit your team and the broader community served by the North West District.\\
	
	I would be more than happy to chat further to discuss my application and am available at your convenience to provide any further information you require by phone or email on the contact details listed above.\\
	Looking forward to your hearing from you.\\
	\\
	Yours Sincerely,\\

	\\
	\\
	\\
	\\
	Benjamin Parry\\
	0456 066 328}

