% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section compétences
\sectionTitle{Skills}{\faTasks}

\begin{keywords}
		\keywordsentry{Project Management}{Agile project management, trained in Freyssinet PM+ project management (PMBOK equivalent):  commercial offers, negotiating contractual issues, planning, risks analysis, tracking project budgets, personnel and time management, quality management for IT software and solutions delivery. Led delivery of up to 5 simultaneous projects, up to €250,000 with profit margins of 30\%. \\}
		\keywordsentry{Analytics}{Data capture, cleansing, integration and use through statistical analysis and visualisations to provide insights. Prototyping and development of tools in python and R to solve data challenges. Developed risk model for storm water pipe infrastructure based on environmental and land use factors, as well as physical characteristics of pipe to optimise inspection campaigns. Parametrisation and delivery of pavement deterioration models. Building data models in Excel and Power BI to track and analyse forecast against actuals.\\ }
		\keywordsentry{Leadership}{Managing teams of up to 5 software developers, database designers, and electrical and instrumentation engineers, including remotely, to deliver work on time and to specifications. Successfully led change management including organisation wide asset management practices, implementation of supervision and reporting structures, and disaster management data collection processes to meet both internal and external requirements. Selected to represent Noosa Council at Local Government Management Associations Leadership Challenge in 2017. \\}
		\keywordsentry{Communication}{Successful work history with people from diverse disciplines and backgrounds in both national and international environments. Able to communicate ideas clearly and logically to ensure efficient teamwork. Part of a team that won the Vinci Innovation Prize for International Dissemination for software developed through collaboration with multiple clients\\}
		\keywordsentry{Reporting}{Financial and performance reporting to management and executives, preparation of project documentation for large-scale, international projects, preparation of project experience returns to ensure insights transferred to both management and peers. Development and implementatin of reporting dashboards and executive reports for clients. Presenting project updates and delivering training sessions to clients and their sub-contractors, with largest involving 100 sub-contractors\\}
		\keywordsentry{Engineering}{Delivering and implementing strategic and operational asset management solutions. Business process owner/system administrator in local council. Analysis of survey data, implementation and parametrisation of deterioration models. Preparation of asset inventory manuals, inspection and maintenance plans. Structural and civil design, including  roads, stormwater, subdivisions, and retaining structures for development applications and detailed construction certificate plans.  \\}
		\keywordsentry{Software}{
		\begin{itemize}
                 \item \textbf{Programming languages} (R, Python, VB.net), 
                 \item \textbf{Enterprise systems} Microsoft SQL, Access, Office, Project, Excel, ERPs, Technology One 
		\item \textbf{Engineering and CAD software} (SMEC PMS, ScanPrint IMS, Civil CAD, AutoCAD, SIDRA, MUSIC, XP-Rafts, STRAND7, Space Gass)
                 \item \textbf{Web development} (Silverlight, HTML5), 
                 \item \textbf{GIS} (QGIS, ArcGIS) 

                 \end{itemize}}
\end{keywords}


%\textbf{Java} (\textbf{JEE}, \textbf{JSE}, JME, Java Card Platform), Microsoft .Net (\textbf{C\#}), \textbf{Typescript}, Javascript, CSS}