% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)





\par{Dear Ms Pigg,\\
	
	I am applying for the Senior Development Manager position at Powerlink. I bring proven experience in leading early-stage infrastructure development where regulatory approvals, land access, stakeholder engagement, and social license determine whether projects can progress to delivery.\\
	
	In my current role as Principal Engineer (Investment Planning) with Transport and Main Roads, I manage upstream development activities for major transport projects under the PAF and OnQ frameworks. This includes preparing strategic assessments, preliminary evaluations, options analyses and business cases. I coordinate specialist inputs across environmental, cultural heritage, and technical disciplines, ensuring regulatory requirements and stakeholder needs are addressed before projects advance to design and delivery.\\
	
	At RECOR, I led urban development projects through concept, plannings approval, detailed design and delivery overseeing the full development lifecycle. This required coordinating and managing environmental consultants, geotechnical and transport investigations, cultural heritage assessments, and securing council and state regulatory approvals. I developed integrated ISO-certified quality, safety and environmental systems to strengthen governance and compliance, while engaging with community stakeholders to secure support for project outcomes. These experiences taught me how to navigate complex approval pathways, balance competing interests, and maintain project momentum through regulatory processes—capabilities directly relevant to Powerlink’s upstream development.\\
	
	Throughout my career I have built and maintained relationships with government agencies, local councils, Indigenous groups and community stakeholders. At TMR, I have engaged across departments and with Traditional Owners on cultural heritage and native title considerations. At VINCI in France, I managed stakeholder engagement across international jurisdictions, working with regulators and communities to progress large-scale infrastructure projects. I understand that development success depends on trust, transparency, and genuine respect for diverse community perspectives.\\
	
	I have also managed procurement of specialist services, overseen consultant contracts, coordinated technical deliverables, and reported to executives on development progress, risks and stakeholder outcomes. My experience demonstrates the discipline required to keep development activities on track while managing budgets, schedules, and governance requirements.\\
	
	The Senior Development Manager role excites me because it sits at the intersection of strategic thinking, program leadership and community impact—areas where I do my best work. I am ready to lead upstream development activities that set major transmission projects up for success, and I am committed to doing so with integrity, transparency and respect for Queensland communities.\\
	
	I would welcome the opportunity to discuss how my skills and experience can support Powerlink’s vision for a reliable, sustainable energy future.\\
	
	Yours sincerely,\\
	
	Benjamin Parry\\
	0456 066 328}


