% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Career}{\faSuitcase}

%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \consultantexperience
    {Present}   {Information Analyst}{\weblink{https://www.usc.edu.au}{University of the Sunshine Coast}}{Sunshine Coast}
    {July 2018}  {Australian University}{Strategic Information and Analysis Unit}
    {Responsible for the Student Load and Income Forecasting model, undertaking data analysis and reporting.
                  \begin{itemize}
		\item Developing tools in Python, R and excel to manipulate, transform and analyse data.
		\item Preparation of income forecasts, tracking university performance and executive reporting.
		\item Preparation of submissions Australian Government for Commonwealth funding.
		\item Maintenance of interim data warehouse (MS Access) until it is fully replaced.
		\item Collaborating with Marketing teams to assess trends and build market intelligence 
		\item Working closely with Data Warehouse team and help with functional requirements and UAT testing of new data warehouse elements.
		\item Requirements analysis and development to build PowerBI reports to respond to internal needs.
                                                              
                      \end{itemize}
                     \textit{Reason for leaving: returning to engineering}  
                    }
                    {SQL, Excel, Python, Power BI, Forecasting, MS Access}
  \emptySeparator
  \consultantexperience
    {July 2018} {Technical Officer - Asset Systems}{\weblink{https://www.noosa.qld.gov.au}{Noosa Council}}{Noosa}
    {July 2016}   {Local Council for the Noosa Shire}{Asset Management team}
      {Business Owner for Council's strategic asset management systems.
                      \begin{itemize}
		\item Preparation of the Asset Information Management Strategy to structure data collection processes used in the organisation to collect consistent and valuable asset and works data, and integrate with other departments.
		\item Responsible for pavement survey data integration and pavement deterioration modelling in SMEC.
		\item Development and analysis of risk-based model of stormwater network pipe failure  to help coordinate inspection campaigns.
		\item Importing and transformation of spatial data from new developments to visualise, locate, identify and categorise within the asset management system.
		\item Building confidence in asset management across the organisation by working with engaging all with all departments providing awareness sessions.
		\item Implemented disaster information collection process for the National Disaster Relief and Recovery Arrangements for disaster funding and presentation of process at Technology One Local Government conference.                                
                      \end{itemize}
                       \textit{Reason for leaving: Seeking to solidify data science skills}
                    }
                    {Asset information, R, Python, Excel, QGIS, Optimisation models, Deterioration model, SAM, SMEC PMS, MapInfo}
  \emptySeparator
  
  \consultantexperience
    {March 2016}     {It Project Manager (Asset Management)}{\weblink{https://www.vinci.com/vinci.nsf/en/index.htm}{VINCI SA}  \ - \weblink{http://www.soletanchefreyssinet.com}{Soletanche-Freyssinet}}{Paris, France}
    {October 2012}   {Global construction with expertise in specialised building, civil, hydraulic, and electrical engineering}{Advitam Group}
      {Technical lead and project manager for international asset systems and solutions.
                      \begin{itemize}
                     \item Managing up to 5 projects following agile style methodology (Freyssinet PM+) for project life cycle.
		\item Administration of clients database: Building queries, stored procedures and functions to manipulate and use client data to meet their business requirements. 
		\item Implementation of pavement deterioration modelling for highway concessions and pavement survey data management.
		\item Coordinating and building web applications using VB.net, MS SilverLight and HTML5 to connect to databases and structure client processes around asset management in Agile environment.
   		\item Specification and delivery for structural monitoring data capture instruments and analysis of outputs.
		\item Undertaking analysis and building custom reporting in SSRS.
		\item Manipulation and transformation of spatial data using QGIS to visualise and locate client assets.
		\item Delivering presentations, and coordinating and leading training sessions with clients.
		\item Commercial representation at conferences, and preparation of offers and bid submissions.
                      \end{itemize}
                    \textit{Reason for leaving: Return to Australia}
                    }
                    {Project management,  Aglie Projects,  SQL, Data Analysis, SSRS, Deterioration model,  Forecasting, VB.Net, GIS}
  \emptySeparator
  
  \consultantexperience
  {October 2012}       {Civil Engineer}{\weblink{https://ndc.com.au}{Newton Denny Chapelle}}{Lismore}
  {March 2010}      {Town Planning/Civil Engineering/Surveying consultancy for industrial, residential and commercial developments.}{Civil Engineering}
                    {Undertaking preliminary and detailed engineering analyses and designs and managing consulting projects.
           \begin{itemize}

		\item Stormwater modelling and design using MUSIC, CivilCAD and XP-RAFTS and preparation of design plans and documentation.
		\item Civil design including subdivisions, earthworks, pavement, stormwater and services.
		\item Preparation and submissions of technical reports to support development applications.
		\item Ensuring conformity with all relevant standards and regulations in design and supervision of construction quality.
		\item Negotiating development approval conditions and requirements on behalf of the client.
               \end{itemize}
                    \textit{Reason for leaving: Downturn in available work}
                    }
                    {Civil design, Project management, Stormwater modelling, Pavement design, CivilCAD, MUSIC, XP-Rafts }
  \emptySeparator
  \consultantexperience
  {November 2008}      {Structural Engineer}{\weblink{https://www.ghd.com/en-au/index.aspx}{GHD Engineering}}{Brisbane}
  {December 2007}      {Engineering company in water, energy and resources, environment, property and buildings, and transportation.}{Mining \& Industrial Structures department}
   { Part-time - Undergraduate engineer modelling and preparing designs and project specifications.
                    
        \begin{itemize}
		\item Engineering modelling and design using Space Gass and STRAND7.
		\item Preparation of technical specifications and project documentation and design criteria.
               \end{itemize}
                    \textit{Reason for leaving: Completing studies overseas}
                    }
                    {Structural Engineering, STRAND, Space Gass} 
  \emptySeparator   
  \consultantexperience
  {November 2007}    {Civil/Structural Engineer}{Trackstar Alliance}{Brisbane}
  {July 2006}       {Alliance between Queensland Rail, Thiess, United Group, Connell Wagner and Maunsell AECOM to rail projects in SEQ.}{Connell Wagner}
  		{Part-time - work experience role preparing structural designs and rail alignments for a rail duplication project.                 
                      \begin{itemize}
		\item Design of retaining walls, slabs and rail bridges and alignments
		\item Site Supervision during service location and site preparation
                      \end{itemize}
                    \textit{Reason for leaving: Gaining different experience}
                    }
                    {Structural Design,Site Supervision}   
  \emptySeparator            
\end{experiences}
