% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Ben Parry
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section compétences
% Ensure proper hyphenation behavior globally (optional)
\hyphenpenalty=50
\exhyphenpenalty=50

\sectionTitle{Skills}{\faTasks}

\begin{keywords}
	\raggedright % prevent overfull boxes from justified text
	
	% Reduce label column width if YAAC defines \keywordsentry with two columns.
	% Many YAAC forks define a \setcolumnwidths or \setentrylengths macro; if yours does, uncomment and adjust:
	% \setlength{\leftcolwidth}{0.22\textwidth} % make label column a bit narrower
	% \setlength{\rightcolwidth}{0.72\textwidth} % give the text more room
	
	\keywordsentry{Project Investment Planning}{
		Extensive experience leading early-stage project development through structured stage-gate governance frameworks (ATAP, OnQ, PAF). Skilled in problem definition, strategic needs assessment, pre-feasibility studies, options analysis, and business case preparation. Proven ability to coordinate multidisciplinary inputs - technical, commercial, operational, and risk - to produce robust, evidence-based investment documentation. Strong understanding of capital program governance, assurance requirements, and decision-making processes for major infrastructure projects.
	}
	
	\keywordsentry{Commercial \& Financial}{
		Experienced in integrating technical, operational, and financial considerations into project development and investment planning. Skilled in interpreting cost estimates, budgets, and financial models to ensure project options are commercially viable and aligned with organisational priorities. Strong understanding of procurement strategies, contract structures, and delivery models that influence project cost, risk, and performance. Able to translate complex engineering inputs into clear financial and risk language for decision-makers.
	}
	
	\keywordsentry{Multi-disciplinary Coordination}{
		Proven track record coordinating diverse specialist inputs across engineering (civil, structural, electrical, instrumentation, traffic, geotechnical, environmental), operations, finance, and risk. Experienced facilitating workshops on scope definition, risk assessment, cost validation, and schedule development. Adept at synthesising complex information into integrated project documentation and clear, defensible investment recommendations.
	}
	
	\keywordsentry{Project \& Program Management}{
		Proven success delivering complex infrastructure projects and programs using PMBOK, PRINCE2, and Agile frameworks. Expertise in project planning, risk management, resource allocation, procurement, contract administration, and financial oversight. Experienced managing consultants, contractors, and multidisciplinary teams to achieve scope, cost, schedule, and quality objectives in regulated, safety-critical environments.
	}
	
	\keywordsentry{Stakeholder Engagement}{
		Strong communicator skilled in engaging executives, government agencies, asset managers, and project delivery teams. Experienced facilitating collaborative decision-making, aligning competing priorities, and influencing investment outcomes. Proven ability to prepare and present executive briefings, business cases, and technical reports that distil complexity into clear, actionable recommendations.
	}
	
	\keywordsentry{Risk \& Governance}{
		Deep understanding of risk-based decision-making and capital governance frameworks. Experienced conducting risk assessments, developing mitigation strategies, and supporting stage-gate assurance processes. Implemented ISO 9001, 45001, and 14001 management systems. Strong commitment to probity, transparency, and disciplined governance across program delivery and investment planning.
	}
	
	\keywordsentry{Technical Engineering }{
		Chartered Civil Engineer (RPEQ, CPEng, NER) with broad infrastructure experience spanning transport, civil structures, stormwater, and urban development. Combines engineering judgment with analytical capability to support sound, data-driven decision-making. Understanding of asset management, operational performance, and maintainability principles that underpin sustainable infrastructure investment.
	}
	
	\keywordsentry{Software \& Systems}{
		\begin{itemize}[leftmargin=*]
			\item \textbf{Project Management:} MS Project, Primavera, 3PCM
			\item \textbf{Business Analysis:} Excel (advanced financial modelling), Power BI, Tableau
			\item \textbf{Engineering:} 12D, AutoCAD, MUSIC, TUFLOW, Drains, Circly
			\item \textbf{Data Analytics:} R, Python, SQL, QGIS
			\item \textbf{Enterprise Systems:} SAP, TechnologyOne
		\end{itemize}
	}
	
\end{keywords}


	%	\keywordsentry{Leadership \& Governance}{Experienced leader of multidisciplinary teams and sub-consultants, with proven capability in governance, probity, and risk management. Implemented organisation-wide ISO 9001, 45001 and 14001 management systems to embed quality, safety and environmental standards.\\}
		
%		\keywordsentry{Project Development}{Extensive experience in upstream development of major infrastructure projects under ATAP, OnQ and PAF frameworks. Skilled in preparing strategic assessments, options analyses, business cases and planning documentation to secure investment and regulatory approvals.\\}
		
	%	\keywordsentry{Regulatory Approvals}{Proven ability to navigate complex approvals processes including EPBC, native title and cultural heritage frameworks. Experienced in coordinating assurance reviews, planning gates, and interagency approvals to enable project progression.\\}
		
	%	\keywordsentry{Stakeholder Engagement}{Skilled in engaging with regulators, government agencies, Indigenous groups, community stakeholders and delivery partners. Adept at influencing outcomes, building trust, and managing sensitive issues with professionalism and integrity.\\}
		
	%	\keywordsentry{Project \& Program Management}{Proven track record delivering large, complex projects using PMBOK, PRINCE2 and Agile principles. Expertise in procurement, contract administration, financial oversight, schedule and program management across transport, civil structures and urban development.\\}
		
	%	\keywordsentry{Technical Capability}{Chartered Civil Engineer with background in design and delivery of transport, stormwater, road, and subdivision infrastructure. Strong understanding of traffic and transport planning, asset management principles, and whole-of-life cost assessments.\\}
		
	%	\keywordsentry{Reporting \& Communication}{Experienced in preparing clear reports, business cases, and executive briefings. Skilled in presenting at technical reviews, chairing stakeholder forums, and preparing submissions for regulators and funding bodies.\\}
		

	
	
	
%		\keywordsentry{Leadership \& Change Management}{Proven ability to manage teams and resources to deliver projects on time and to specifications. Successfully led change management including organisation wide asset management practices. Establishment \& implementation of organisational ISO management systems for Quality, Environment and Health and Safety. \\}
%	\keywordsentry{Project \& Program Management}{Proven track record delivering complex infrastructure projects using Agile, PMBOK and PRINCE2 frameworks. Experience spans contract administration, commercial negotiations, risk management, delivery and financial oversight. Skilled in managing multi-year programs across road and drainage networks and civil structures, with focus on schedule performance, resource allocation and quality control. \\}
%	   \keywordsentry{Project Development}{Experienced lead for early-stage development of major infrastructure projects through planning and concept design ensuring smooth transition to detailed design and construction. Delivering projects in line with ATAP, OnQ and PAF frameworks. Skilled in preparing business cases, options analyses, and planning documentation to secure investment and regulatory approvals. \\}
%	\keywordsentry{Stakeholder Engagement}{Skilked in engaging with diverse stakeholders in complex and challenging environments. Experienced with engaging with regulators, government agencies, community and indigenous groups and other delivery partners influencing outcomes, building trust, and managing sensitive or high-risk matters with professionalism.\\}
%	  \keywordsentry{Regulatory Approvals \& Governance}{Proven ability to navigate complex approvals processes including planning gates, assurance assessment, environmental, cultural heritage and legislative requirements (EPBC, MID, native title frameworks). Strong focus on compliance, risk management, and transparent governance. \\}
%	\keywordsentry{Civil Engineering}{Civil engineering design for urban developments including roads, stormwater, earthworks and associated infrastructure for design and construction of subdivision, residential, commercial and industrial development. Understanding of traffic and transport planning principles, land-use integration, level of services concepts, demand generation and traffic modeling. Road safety and speed limit reviews. Environmental and sustainability impacts in projects. \\}
%		\keywordsentry{Asset Management}{Preparation of asset inventory manuals, inspection and maintenance plans for strategic and operational asset management for highway concessions and local government road and stormwater networks. Deterioration modelling for bridges and pavement. High level condition modelling and analysis and program management. Whole of life costings, value for money and cost-benefit analyses. \\}
%   \keywordsentry{Reporting \& Communication}{Proven ability to prepare clear, concise reports, submissions and presentations for executives, sponsors, and external regulators. Experienced in chairing stakeholder forums, technical reviews and interagency consultations. \\}
%		\keywordsentry{Analytics}{Data capture, cleansing, integration and use through statistical analysis and visualisations to provide insights and decision making aids with focus on risk management.\\ }






