% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional Career}{\faSuitcase}

%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}

\consultantexperience
  {Present} {Principal Engineer (Investment Planning)}{\weblink{https://www.tmr.qld.gov.au}{Transport and Main Roads}}{North Coast Region}
  {May 2025} {State Roads Authority}{Investment Planning}
  {
    \begin{itemize}
\item Led early-stage planning of major transport infrastructure projects, coordinating multidisciplinary specialists and managing consultants to deliver project development aligned with government frameworks (ATAP, OnQ, PAF).
\item Directed procurement and contract management of technical services, ensuring probity, value-for-money and compliance with governance requirements.
\item Provided strategic advice to senior executives on development progress, risks and stakeholder engagement to support investment decision-making.
    \end{itemize}
  }
  {Project Planning, Stakeholder Engagement, Procurement, Contract Management, Governance} 
 	\emptySeparator 
\consultantexperience
  {May 2025}    {Senior Engineer (Civil)}{\weblink{https://www.tmr.qld.gov.au/}{Transport and Main Roads}}{North Coast Region}
  {December 2023}   {State Roads Authority}{Maintenance, Assets \& Traffic Engineering team}
  {                 
  
    \begin{itemize}
     \item Led strategic asset management for regional portfolio of 1,000+ bridges, major culverts and fabricated steel traffic structures valued at \$2.5 billion, balancing asset integrity, safety, lifecycle costs and network reliability.
     \item Developed asset performance analysis frameworks integrating structural condition data, risk profiles and deterioration modeling to inform \$5 million annual maintenance and capital investment programs.
     \item Directed procurement, contract administration and delivery of structural remediation projects, managing consultants and contractors to ensure quality, compliance and value-for-money outcomes within budget and schedule.
     \item Led technical reviews of inspection data and condition assessments, applying engineering judgment to prioritize interventions, optimize resource allocation and maintain network performance.
     \item Managed heavy vehicle access approvals (Class 1 \& 2) and structure management plans, conducting risk assessments that balanced asset condition, safety requirements and freight industry needs.
     \item Coordinated multidisciplinary specialists (structural, geotechnical, environmental) and engaged with Indigenous partners to address cultural heritage and native title considerations in asset remediation projects.
     \item Active member of TMR's statewide Structures Maintenance Program Leadership Team, contributing to asset management strategy, prioritization frameworks and governance of bridge and culvert programs.
     \item Applied asset management standards and frameworks (AS5130, TMR Technical Standards) to ensure continuous improvement and compliance across portfolio management activities.
    \end{itemize}
        \vspace{0.5em}
     \textbf{Higher duty roles (2024-2025):}
    \begin{itemize}
    \item \textbf{Assets (Apr 2025):} Led civil structures asset team, overseeing staff performance, strategic asset planning, stakeholder engagement and cross-business coordination of portfolio management activities.
    \item \textbf{Design – Technical Services (May 2024):} Reviewed and approved technical designs for compliance with TMR standards, assessing structural adequacy, safety and operational requirements.
    \end{itemize}
    \vspace{0.5em}
  }
  {Asset Management, Lifecycle Planning, Condition Assessment, Risk Management, Deterioration Modelling, Program Management, Procurement, Contract Administration, Stakeholder Engagement, Civil Structures}
 	\emptySeparator 
 
   \consultantexperience
	{November 2023}    {Senior Engineer (Civil)}{\weblink{https://recor.au}{RECOR}}{Noosa}
	{June 2021}   {Civil/Structural Engineers \& Project Managers.}{Civil Engineering team}
	{                  
		\begin{itemize}
			\item Established and led the civil engineering discipline within the organisation, providing RPEQ supervision and mentoring for junior engineers and designers.
			\item Managed multidisciplinary projects from concept to delivery, overseeing contracts, financial control, regulatory approvals, and stakeholder engagement.
			\item Directed multidisciplinary sub-consultants (surveyors, transport modellers, geotechnical, environmental, hydraulic, electrical) to integrate specialist inputs and align outcomes with planning approvals and delivery requirements.
			\item Coordinated with local councils, government agencies and contractors to secure approvals, manage community expectations, and ensure projects met environmental and network requirements.
			\item Developed and implemented ISO-certified quality, safety and environmental management systems, embedding governance rigour across operations.
			\item Delivered stormwater, road, and earthworks infrastructure design and construction, ensuring compliance with technical and regulatory standards.
			\item Prepared clear technical reports, documentation and submissions to support approvals and stakeholder decision-making.
\end{itemize}
}
{Civil Engineering, Urban Development, Leadership, Project Governance, Stakeholder Engagement, Design \& Modelling, Project Management}
	\emptySeparator   
  
  \consultantexperience
  {June 2021}    {Project Management Engineer}{\weblink{https://www.pavement.com.au}{Pavement Management Services}}{Sunshine Coast}
  {October 2020}   {Specialist engineers in pavement solutions.}{Network Projects team}
  {                 
    \begin{itemize}
\item Managed network-level pavement condition assessment and asset management projects for local and state government clients, delivering on scope, budget and quality requirements.
\item Developed pavement deterioration models and capital works programs, integrating condition data, lifecycle analysis and budget constraints to optimize renewal timing and maximize asset value.
\item Provided specialist technical advice on pavement performance, condition assessment methodologies and asset management frameworks to support value-for-money infrastructure investment decisions.
\item Led stakeholder engagement with government agencies, consultants and contractors to align project requirements, manage expectations and deliver collaborative outcomes.
\item Managed project quality plans, financial reporting and contract administration, ensuring compliance with specifications and client standards.
    \end{itemize}
  }
  {Asset Management, Project Management, Deterioration Modelling, Condition Assessment, Pavement Networks, Technical Advisory, Stakeholder Engagement}
  
  \emptySeparator 
  \consultantexperience
    {October 2020}   {Information Analyst}{\weblink{https://www.usc.edu.au}{University of the Sunshine Coast}}{Sunshine Coast}
    {July 2018}  {Australian University}{Strategic Information and Analysis team}
    {
        \begin{itemize}
\item Led development of strategic forecasting models and predictive analytics frameworks using R and Python, supporting executive decision-making and government funding submissions.
\item Transformed complex datasets into actionable insights through statistical analysis, data visualization and business intelligence dashboards, enabling evidence-based resource allocation and risk management.
\item Engaged with senior stakeholders across departments to define requirements, validate analytical outputs and align performance reporting with organizational objectives.
\item Built automated data pipelines and reporting tools to improve data quality, reduce manual processing and enhance decision-making capability across the institution.
        \end{itemize}
      }
      {Data Analytics, Predictive Modelling, Statistical Analysis, Business Intelligence, Performance Reporting, R, Python, Stakeholder Engagement}
	  
  \emptySeparator
 \consultantexperience
    {July 2018} {Technical Officer}{\weblink{https://www.noosa.qld.gov.au}{Noosa Council}}{Noosa}
    {July 2016}   {Local Council for the Noosa Shire}{Asset Management team}
      {
        \begin{itemize}
\item Led strategic asset management for council road and stormwater networks, coordinating operational teams, contractors and senior management to deliver risk-based inspection and renewal programs.
\item Managed pavement management system operations including deterioration modeling, condition analysis and development of 5-year capital works program, integrating technical data with budget constraints to optimize intervention strategies.
\item Developed spatial risk-based model for stormwater network management, integrating environmental factors, structural condition, land use and preliminary inspection data to prioritize inspection campaigns and mitigate asset failure risks.
\item Directed procurement processes including tender preparation, evaluation and contract administration, ensuring value-for-money outcomes and effective contractor performance management.
\item Led cross-departmental change management to implement asset management frameworks and information standards, securing stakeholder buy-in and embedding strategic asset practices across the organization.
\item Coordinated disaster management information systems and NDRRA funding processes, ensuring compliance with legislative requirements and accurate capture of asset damage data.
        \end{itemize}
      }
      {Asset Management, Risk Modelling, Deterioration Modelling, Network Optimization, Procurement, Contract Management, Stakeholder Engagement, Change Management}
	  
  \emptySeparator
\consultantexperience
    {March 2016}     {Project Manager (Asset Management)}{\weblink{https://www.vinci.com/vinci.nsf/en/index.htm}{VINCI SA} \ - \weblink{http://www.soletanchefreyssinet.com}{Soletanche-Freyssinet}}{Paris, France}
    {October 2012}   {Global construction company with expertise in specialised building, civil, hydraulic, and electrical engineering}{Asset Solutions team}
      {
        \begin{itemize}
\item Led international asset management projects across Europe, Middle East and North America, delivering strategic asset management solutions for government agencies and concession operators managing major bridge, tunnel, highway and water infrastructure.
\item Developed comprehensive inspection and maintenance plans, asset management frameworks and lifecycle strategies for signature infrastructure, integrating condition assessment, risk analysis and performance optimization.
\item Managed structural health monitoring programs including specification and procurement of instrumentation systems, data analysis and reporting to inform long-term asset strategies and intervention planning.
\item Coordinated multidisciplinary engineering teams and subcontractors across complex international projects, managing scope, schedule, cost and quality to deliver client outcomes.
\item Delivered technical training, workshops and presentations to client asset management teams, embedding new processes, systems and continuous improvement practices.
\item Applied project management frameworks (PMBOK, PRINCE2, Agile) to deliver structured risk, cost and schedule management across diverse infrastructure asset portfolios.
\item Winner, 2015 Vinci Innovation Prize for International Dissemination for development of mobile asset information system enabling field staff to access real-time asset data and work instructions.
         \end{itemize}
        }
        {Asset Management, Project Management, Lifecycle Planning, Structural Monitoring, Condition Assessment, International Projects, Contract Management, Technical Leadership}
		
  \emptySeparator
  \consultantexperience
  {October 2012}       {Civil Engineer}{\weblink{https://ndc.com.au}{Newton Denny Chapelle}}{Lismore}
  {March 2010}      {Civil engineering consultancy for urban development projects}{Civil Engineering team}
    {
      \begin{itemize}
\item Delivered civil engineering design and technical reporting for urban development projects, ensuring compliance with planning requirements and engineering standards.
\item Coordinated with consultants, contractors and councils to secure regulatory approvals and deliver infrastructure projects from concept through construction.
      \end{itemize}
    }
    {Civil Design, Project Delivery, Regulatory Compliance, Stakeholder Coordination}
  \emptySeparator            
\end{experiences}
